---
title: "Scale Score"
author: "Jessica pardim Araujo"
date: "2/16/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library (tidyverse)
library (psych)
library (readr)
library (mosaic)
zoom_premeasures <- read_csv("Zoom and Self-Objectification Premeasures.csv")
Zoom_daily <- read_csv("Zoom and Self-Objectification Daily.csv")
dailyscalescorespt1 <- read_csv("dailyscalescorespt1.csv")
premeasurescalescores <- read_csv ("premeasurescalescores.csv")

```

## Authenticity 

```{r}

corr.test(select(Zoom_daily, SSO_4, SSO_5))$r

alpha(select(Zoom_daily, SSO_4, SSO_5))

Zoom_daily$authenticity <- rowMeans(select(Zoom_daily, SSO_4, SSO_5), na.rm = TRUE)

favstats(Zoom_daily$authenticity)

qplot(x = authenticity, data = Zoom_daily, bins = 8)

```

## Interaction Quality (reversed happy feelings)

```{r}
  
corr.test(select(Zoom_daily,interact_comfort,interact_anxious,interact_happy,interact_unhappy, interact_friendly,interact_warm,interact_easygoing,interac_hostile,interact_sincere,interact_authentic,interact_apprehensiv,interact_cooperative,interact_aggresive ))$r

Zoom_daily <- Zoom_daily %>%
  mutate(interact.r_comfort = (1 + 7) - interact_comfort) %>% 
  mutate(interact.r_happy = (1 + 7) - interact_happy) %>% 
  mutate(interact.r_friendly = (1 + 7) - interact_friendly) %>% 
  mutate(interact.r_warm = (1 + 7) - interact_warm) %>%
  mutate(interact.r_easygoing = (1 + 7) - interact_easygoing) %>% 
  mutate(interact.r_sincere = (1 + 7) - interact_sincere) %>%  
  mutate(interact.r_authentic = (1 + 7) - interact_authentic) %>% 
  mutate(interact.r_cooperative = (1 + 7) - interact_cooperative) 
```

#interact_neg
```{r}
corr.test(select(Zoom_daily,interact.r_comfort,interact_anxious,interact.r_happy,interact_unhappy, interact.r_friendly,interact.r_warm,interact.r_easygoing,interac_hostile,interact.r_sincere,interact.r_authentic,interact_apprehensiv,interact.r_cooperative,interact_aggresive))$r

alpha(select(Zoom_daily,interact.r_comfort,interact_anxious,interact.r_happy,interact_unhappy, interact.r_friendly,interact.r_warm,interact.r_easygoing,interac_hostile,interact.r_sincere,interact.r_authentic,interact_apprehensiv,interact.r_cooperative,interact_aggresive))

Zoom_daily$interaction_neg <- rowMeans(select(Zoom_daily,interact.r_comfort,interact_anxious,interact.r_happy,interact_unhappy, interact.r_friendly,interact.r_warm,interact.r_easygoing,interac_hostile,interact.r_sincere,interact.r_authentic,interact_apprehensiv,interact.r_cooperative,interact_aggresive), na.rm = TRUE)

favstats(Zoom_daily$interaction_neg)

qplot(x = interaction_neg, data = Zoom_daily, bins = 10)
```


## Daily SSO (state of self-obejtification)

```{r}

corr.test(select(Zoom_daily, SSO_1, SSO_2, SSO_3))$r

alpha(select(Zoom_daily, SSO_1, SSO_2, SSO_3))

Zoom_daily$daily_SSO <- rowMeans(select(Zoom_daily, SSO_1, SSO_2, SSO_3), na.rm = TRUE)

favstats(Zoom_daily$daily_SSO)

qplot(x = daily_SSO, data = Zoom_daily, bins = 10)

Zoom_daily <- Zoom_daily %>% 
  mutate(Self_Obj = ifelse(daily_SSO == 1, 0, 1))

Zoom_daily$Self_Obj

```

# Stroop Daily Mental Fatigue 

## Stroop Test
# stroop is teh measure of cogn fatigue

```{r}

glimpse (Zoom_daily)

Zoom_daily <- Zoom_daily %>% 
  mutate(stroop = `StroopTime_Incongru_Page Submit` - `StroopTime_Congrue_Page Submit`)

#remove greater than 100 or less than -100
Zoom_daily <- Zoom_daily %>% 
  filter (stroop <= 40) %>% 
  filter (stroop >= -100)

ggplot (Zoom_daily, aes(stroop)) + 
  geom_boxplot()

```


#Daily Well Being 

## State Self-esteem (should separate positive and negative?)

```{r}
corr.test(select(Zoom_daily,SES_Satisfied,SES_Bad,SES_Good,SES_Competent,SES_Proud,SES_Useless,SES_Worth,SES_Respect,SES_Failure,SES_Positive))$r

##reverse negative ones 

Zoom_daily <- Zoom_daily %>%
  mutate(SES.r_Satisfied = (1 + 4) - SES_Satisfied) %>% 
  mutate(SES.r_Good = (1 + 4) - SES_Good) %>% 
  mutate(SES.r_Competent = (1 + 4) - SES_Competent) %>% 
  mutate(SES.r_Worth = (1 + 4) - SES_Worth) %>%
  mutate(SES.r_Positive = (1 + 4) - SES_Positive)
```

```{r}
corr.test(select(Zoom_daily,How_Today,SES.r_Satisfied,SES_Bad,SES.r_Good,SES.r_Competent,SES_Proud,SES_Useless,SES.r_Worth,SES_Respect,SES_Failure,SES.r_Positive))$r

alpha(select(Zoom_daily,SES.r_Satisfied,SES_Bad,SES.r_Good,SES.r_Competent,SES_Proud,SES_Useless,SES.r_Worth,SES_Respect,SES_Failure,SES.r_Positive))

Zoom_daily$SES_daily <- rowMeans(select(Zoom_daily,SES.r_Satisfied,SES_Bad,SES.r_Good,SES.r_Competent,SES_Proud,SES_Useless,SES.r_Worth,SES_Respect,SES_Failure,SES.r_Positive), na.rm = TRUE)

favstats(Zoom_daily$SES_daily)

qplot(x = SES_daily, data = Zoom_daily, bins = 12)
```

## How was today? (How to score one variable?)

# do nothing 
```{r}

favstats(Zoom_daily$howtoday_score)

qplot(x = How_Today, data = Zoom_daily, bins = 5.5)

Zoom_daily$How_Today

```


## Mental Fatigue


```{r}

Zoom_daily <- Zoom_daily %>% 
  mutate(Mental_Fatigue = (Mental_Fatigue -1)/2) %>% 
  mutate(ConcentrateDifficult = (ConcentrateDifficult -1)/2) %>% 
  mutate(Memory_Problems = (Memory_Problems -1)/2) %>% 
  mutate(Slowness_of_Thinking = (Slowness_of_Thinking -1)/2) %>% 
  mutate(Sensitivity_to_Stres = (Sensitivity_to_Stres -1)/2) %>% 
  mutate(Irritability = (Irritability -1)/2)

corr.test(select(Zoom_daily, Mental_Fatigue, ConcentrateDifficult, Memory_Problems, Slowness_of_Thinking, Sensitivity_to_Stres, Irritability))$r
  

grep("Irritability", colnames(Zoom_daily))

33- 38

```


```{r}
alpha(select(Zoom_daily, Mental_Fatigue, ConcentrateDifficult, Memory_Problems, Slowness_of_Thinking, Sensitivity_to_Stres, Irritability))

Zoom_daily$Fatigue_daily <- rowMeans(select(Zoom_daily, Mental_Fatigue, ConcentrateDifficult, Memory_Problems, Slowness_of_Thinking, Sensitivity_to_Stres, Irritability), na.rm = TRUE)

favstats(Zoom_daily$Fatigue_daily)

qplot(x = Fatigue_daily, data = Zoom_daily, bins = 12)
```




## Physical Fatigue (there is only one variable for physical fatigue, and it is on Mental fatique Scale block )



