---
title: "Zoom_MR_MLM"
author: "Jessica pardim Araujo"
date: "2/8/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(readr)
library (rio)
library(broom)
library(car)
library(lme4)
library(lmerTest)
premeasurescalescores <- read_csv("premeasurescalescores.csv")
dailyscalescorespt1 <- read_csv("dailyscalescorespt1.csv")
```


```{r}

zoom_premeasures %>%
group_by(Race) %>% #do calculations by siteID
summarize(total = n() / 56 *100 ) 


favstats(zoom_premeasures$Age)

qplot(zoom_premeasures$Race)


```



```{r}
#daily_SSO log

Zoom_daily$lg_daily_SSO <- log(Zoom_daily$daily_SSO+1)

#Daily state self objectification - State self-esteem

 ggplot(Zoom_daily, aes(lg_daily_SSO,SES_daily ))+
   geom_point()+
   geom_smooth(method = "lm")
 
 ggplot(Zoom_daily, aes(SES_daily))+
   geom_histogram(bins = 15)
 
  ggplot(Zoom_daily, aes(lg_daily_SSO))+
   geom_histogram(bins = 15)
 
#Regression

SSO_SES<-lm(SES_daily~lg_daily_SSO, data=Zoom_daily)
summary(SSO_SES)


#residuals
resid1 <- augment(SSO_SES)
summary(resid1)

ggplot(SSO_SES, aes(.resid))+ 
  geom_histogram(bins=20)

ggplot(SSO_SES, aes(.fitted, .resid))+ 
  geom_point()


#Zoom_daily$cent_SES_daily <- Zoom_daily$SES_daily-mean(Zoom_daily$SES_daily)

 # ggplot(Zoom_daily, aes(daily_SSO,cent_SES_daily ))+
 #   geom_point()+
 #   geom_smooth(method = "lm")

#Authenticity - State self-esteem

 ggplot(Zoom_daily, aes(authenticity,SES_daily ))+
   geom_point()+
   geom_smooth(method = "lm")
 
 ggplot(Zoom_daily, aes(authenticity))+
   geom_histogram(bins = 15)

Auth_SES<-lm(SES_daily~authenticity, data=Zoom_daily)
summary(Auth_SES)


#Authenticity - State self-objectification

 ggplot(Zoom_daily, aes(authenticity,lg_daily_SSO ))+
   geom_point()+
   geom_smooth(method = "lm")
 
  ggplot(Zoom_daily, aes(lg_daily_SSO))+
   geom_histogram(bins = 15)

Auth_SSO<-lm(authenticity~lg_daily_SSO, data=Zoom_daily)
summary(Auth_SSO)

#residuals
resid1 <- augment(Auth_SES)
summary(resid1)

ggplot(Auth_SES, aes(.resid))+ 
  geom_histogram(bins=20)

ggplot(Auth_SES, aes(.fitted, .resid))+ 
  geom_point()

#Daily state self objectification - authenticity - State self-esteem

sso_auth_ses<-lm(SES_daily~lg_daily_SSO + authenticity, data=Zoom_daily)

summary(sso_auth_ses)
```
#holding authenticity to 0
# affect of auth holding SSO at 0
#rel. with sso and self est change depending in how much auth you're feeling 
#take out non sign interaction, in this case is auth.

```{r}
#Mental Fatigue log

#Zoom_daily$lg_Fatigue_daily <- log(Zoom_daily$Fatigue_daily+1)

#Daily state self objectification - daily fatigue

 ggplot(Zoom_daily, aes(daily_SSO,Fatigue_daily ))+
   geom_point()+
   geom_smooth(method = "lm")
 
 ggplot(Zoom_daily, aes(Fatigue_daily))+
   geom_histogram(bins = 15)
 
  ggplot(Zoom_daily, aes(lg_daily_SSO))+
   geom_histogram(bins = 15)
 
#Regression

SSO_fatigue<-lm(Fatigue_daily~daily_SSO, data=Zoom_daily)
summary(SSO_fatigue)


#residuals
resid7 <- augment(SSO_fatigue)
summary(resid7)

ggplot(SSO_fatigue, aes(.resid))+ 
  geom_histogram(bins=20)

ggplot(SSO_SES, aes(.fitted, .resid))+ 
  geom_point()


#Authenticity - Daily fatigue

 ggplot(Zoom_daily, aes(authenticity,Fatigue_daily ))+
   geom_point()+
   geom_smooth(method = "lm")
 
 ggplot(Zoom_daily, aes(authenticity))+
   geom_histogram(bins = 15)

Auth_fatigue<-lm(Fatigue_daily~authenticity, data=Zoom_daily)
summary(Auth_fatigue)


#Daily state self objectification - authenticity - Daily fatigue

sso_auth_fatigue<-lm(Fatigue_daily~lg_daily_SSO + authenticity, data=Zoom_daily)

summary(sso_auth_fatigue)

#Authenticity - Stroop

Stroop_Auth<-lm(stroop~authenticity, data=Zoom_daily)
summary(Stroop_Auth)


ggplot(Zoom_daily, aes(authenticity,stroop ))+
   geom_point()+
   geom_smooth(method = "lm")
 
 ggplot(Zoom_daily, aes(stroop))+
   geom_histogram(bins = 15)
 
 #residuals
resid2 <- augment(Stroop_Auth)
summary(resid2)

ggplot(Stroop_Auth, aes(.resid))+ 
  geom_histogram(bins=10)

ggplot(Stroop_Auth, aes(.fitted, .resid))+ 
  geom_point()

#Daily state self objectification - authenticity - Stroop

sso_auth_stroop<-lm(stroop~daily_SSO + authenticity + daily_SSO*authenticity, data=Zoom_daily)

summary(sso_auth_stroop)
```

```{r}

#Daily state self objectification - How_today

#daily SSO use log

ggplot(Zoom_daily, aes(daily_SSO,How_Today ))+
   geom_point()+
   geom_smooth(method = "lm")

 ggplot(Zoom_daily, aes(How_Today))+
   geom_histogram(bins = 15)

SSO_HOW<-lm(How_Today~daily_SSO, data=Zoom_daily)
summary(SSO_HOW)

 #residuals
resid3 <- augment(SSO_HOW)
summary(resid3)

ggplot(SSO_HOW, aes(.resid))+ 
  geom_histogram(bins=10)

ggplot(SSO_HOW, aes(.fitted, .resid))+ 
  geom_point()

#Authenticity - How_today
 ggplot(Zoom_daily, aes(authenticity,How_Today ))+
   geom_point()+
geom_smooth(method = "lm")
 ggplot(Zoom_daily, aes(authenticity))+
 geom_histogram(bins = 10)
ggplot(Zoom_daily, aes(How_Today))+
   geom_histogram(bins = 7)

Auth_HOW<-lm(How_Today~authenticity, data=Zoom_daily)
summary(Auth_HOW)

#Daily state self objectification - authenticity - How_today
#remove Auth
sso_auth_how<-lm(How_Today~daily_SSO + authenticity, data=Zoom_daily)

summary(sso_auth_how)
```


```{r}
#low R2, plot
#Interaction Quality - Stroop

ggplot(Zoom_daily, aes(interaction_neg,stroop ))+
   geom_point()+
   geom_smooth(method = "lm")

 ggplot(Zoom_daily, aes(interaction_neg))+
   geom_histogram(bins = 15)
 
 
 ggplot(Zoom_daily, aes(stroop))+
   geom_histogram(bins = 15)


inter_stroop<-lm(stroop~interaction_neg, data=Zoom_daily)
summary(inter_stroop)

plot(inter_stroop)

#Daily state self objectification - Interaction Quality - Stroop

sso_inte_stroop<-lm(stroop~daily_SSO + interaction_neg + daily_SSO*interaction_neg, data=Zoom_daily)

summary(sso_inte_stroop)

vif(sso_inte_stroop)




```
#removing outliers 







  #removing 100

Residuals:
     Min       1Q   Median       3Q      Max 
-17.3620  -4.5972  -0.2154   2.9743  17.3221 

Coefficients:
                           Estimate Std. Error t value Pr(>|t|)  
(Intercept)                6.349098   2.711879   2.341   0.0205 *
daily_SSO                 -0.557695   1.091671  -0.511   0.6102  
interaction_neg           -0.002034   0.810943  -0.003   0.9980  
daily_SSO:interaction_neg  0.180960   0.272905   0.663   0.5083  
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1


```{r}
#Interaction Quality - SES

ggplot(Zoom_daily, aes(interaction_neg,SES_daily ))+
   geom_point()+
   geom_smooth(method = "lm")

 ggplot(Zoom_daily, aes(interaction_neg))+
   geom_histogram(bins = 15)

inter_SES<-lm(SES_daily~interaction_neg, data=Zoom_daily)
summary(inter_SES)

#Daily state self objectification - Interaction Quality - SES
#test for VIF

sso_inte_SES<-lm(SES_daily~daily_SSO + interaction_neg + authenticity, data=Zoom_daily)

summary(sso_inte_SES)

#Test VIF

vif_values <- vif(sso_inte_SES)

#create horizontal bar chart to display each VIF value
barplot(vif_values, main = "VIF Values", horiz = TRUE, col = "steelblue")+
abline(v = 5, lwd = 3, lty = 2)


```

```{r}

#Interaction Quality - How_Today

ggplot(Zoom_daily, aes(interaction_neg,How_Today ))+
   geom_point()+
   geom_smooth(method = "lm")

 ggplot(Zoom_daily, aes(How_Today))+
   geom_histogram(bins = 6)

inter_how<-lm(How_Today~interaction_neg, data=Zoom_daily)
summary(inter_how)

#Daily state self objectification - Interaction Quality - How_Today

sso_inte_how<-lm(How_Today~daily_SSO + interaction_neg , data=Zoom_daily)

summary(sso_inte_how)

vif(sso_inte_how)

```

```{r}
#Daily state self objectification - Interaction Quality - How_Today

sso_inte_how<-lm(How_Today~daily_SSO + interaction_neg + daily_SSO*interaction_neg, data=Zoom_daily)

summary(sso_inte_how)

```

```{r}
#Join

Zoom_join<-Zoom_daily %>% 
  left_join(premeasurescalescores, by = "partID")

Zoom_join<-Zoom_join %>% 
  full_join(dailyscalescorespt1, by = "partID")

#Changing date to 0-4

Zoom_join<-Zoom_join %>% 
  mutate(day = (day -1))
  

Zoom_join$day

```

# Multilevel Modeling 


```{r}
#MLM

mlm_mod_int <- lmer(authenticity~Self_Obj +day
                         + (1 + day|partID), 
                         data = Zoom_join)
summary(mlm_mod_int)
plot(mlm_mod_int)
confint(mlm_mod_int)


mlm_mod_int2 <- lmer(Fatigue_daily~Self_Obj +day
                         + (1 + day|partID), 
                         data = Zoom_join)
summary(mlm_mod_int2)

mlm_mod_int3 <- lmer(How_Today~Self_Obj +day
                         + (1 + day|partID), 
                         data = Zoom_join)
summary(mlm_mod_int3)

mlm_mod_int4 <- lmer(interaction_neg~Self_Obj +day
                         + (1 + day|partID), 
                         data = Zoom_join)
summary(mlm_mod_int4)

mlm_mod_int5 <- lmer(stroop~Self_Obj +day
                         + (1 + day|partID), 
                         data = Zoom_join)
summary(mlm_mod_int5)


mlm_mod_int6 <- lmer(SES_daily~Self_Obj +day
                         + (1 + day|partID), 
                         data = Zoom_join)
summary(mlm_mod_int6)

```












