---
title: "zoom_sso_cleaning"
author: "Randi L. Garcia"
date: "5/22/2022"
output: html_document
---

```{r}
library(tidyverse)
library(readr)
library(psych)
```

```{r}
zoom_premeasures <- read_csv("../Data/raw data/SS: Zoom and Self-Objectification Premeasures_May 16, 2021_06.46.csv")
zoom_daily <- read_csv("../Data/raw data/SS: Zoom and Self-Objectification Daily_May 16, 2021_06.45.csv")
```

```{r}
names(zoom_daily)
names(zoom_premeasures)
```

# Demographics

```{r}
zoom_premeasures <- zoom_premeasures %>%
  select(Progress, ResponseId, Age:partID) 

head(zoom_premeasures)
table(zoom_premeasures$Gender) #What to do with nonbinary?
```
```{r}
table(zoom_premeasures$Sexual_Orientation)
table(zoom_premeasures$Race)
table(zoom_premeasures$Political)
```


# Zoom Use

## Weekly and Daily Zoom Use (premeasures)

```{r}
table(zoom_premeasures$Zoom_Use_Weekly)
table(zoom_premeasures$Zoom_Use_Daily)
```

## Self-view and Image Distraction

```{r}
#1 is always hiding self-view and 5 is never. 5 means seeing oneself more.
table(zoom_premeasures$Self_View_Daily)

zoom_premeasures <- zoom_premeasures %>% 
  mutate(Hide_Self_View = 6 - Self_View_Daily,
         Self_View = Self_View_Daily) %>%
  select(-Self_View_Daily)

#In original: 1 is great deal distracted, 5 is not at all
table(zoom_premeasures$Image_Distraction)

zoom_premeasures <- zoom_premeasures %>% 
  mutate(Image_Distraction = 6 - Image_Distraction) #reversing
```


# Trait Self-Objectification 

## Self-Objectification Questionaire (SOQ)

```{r}
zoom_premeasures$ability <- rowMeans(select(zoom_premeasures,SOQ_1, SOQ_2, SOQ_4, SOQ_7, SOQ_9), na.rm = TRUE)
zoom_premeasures$appearance <- rowMeans(select(zoom_premeasures,SOQ_3, SOQ_5, SOQ_6, SOQ_8, SOQ_10), na.rm = TRUE)
```

```{r}
zoom_premeasures <- zoom_premeasures%>%
  mutate(tso_mean = (ability - appearance))

qplot(x=tso_mean, data=zoom_premeasures, bins=8)

zoom_premeasures <- zoom_premeasures %>%
  select(-(SOQ_1:SOQ_10))
```

## OBCS: Surveillance

```{r}
table(zoom_premeasures$OBCS_1)

#reversing items (McKinley & Hyde)
zoom_premeasures <- zoom_premeasures %>%
  mutate(OBCS_1.r = (1+7) - OBCS_1,
         OBCS_2.r = (1+7) - OBCS_2,
         OBCS_3.r = (1+7) - OBCS_3,
         OBCS_4.r = (1+7) - OBCS_4,
         OBCS_7.r = (1+7) - OBCS_7,
         OBCS_8.r = (1+7) - OBCS_8)
```

```{r}
corr.test(select(zoom_premeasures, OBCS_1.r, OBCS_2.r, OBCS_3.r, OBCS_4.r, OBCS_5, OBCS_6, OBCS_7.r, OBCS_8.r))$r

alpha(select(zoom_premeasures, OBCS_1.r, OBCS_2.r, OBCS_3.r, OBCS_4.r, OBCS_5, OBCS_6, OBCS_7.r, OBCS_8.r))
```

```{r}
zoom_premeasures$OBCS_sur <- rowMeans(select(zoom_premeasures, OBCS_1.r, OBCS_2.r, OBCS_3.r, OBCS_4.r, 
                                             OBCS_5, OBCS_6, OBCS_7.r, OBCS_8.r), na.rm = TRUE)

qplot(x=OBCS_sur, data=zoom_premeasures, bins=10)

names(zoom_premeasures)
zoom_premeasures <- zoom_premeasures %>%
  select(-(OBCS_1:OBCS_24), -OBCS_1.r, -OBCS_2.r, -OBCS_3.r, -OBCS_4.r, -OBCS_7.r, -OBCS_8.r)
```

## Social Physique Anxiety Scale

```{r}
#reversing
zoom_premeasures <- zoom_premeasures %>%
  mutate(SPAS_1.r = (1 + 5) - SPAS_1,
         SPAS_2.r = (1 + 5) - SPAS_2,
         SPAS_5.r = (1 + 5) - SPAS_5,
         SPAS_8.r = (1 + 5) - SPAS_8,
         SPAS_11.r = (1 + 5) - SPAS_11)
```

```{r}
corr.test(select(zoom_premeasures, SPAS_3, SPAS_4, SPAS_6, SPAS_7, SPAS_9, SPAS_10, SPAS_12, 
                 SPAS_1.r, SPAS_2.r, SPAS_5.r, SPAS_8.r, SPAS_11.r ))$r

alpha(select(zoom_premeasures, SPAS_3, SPAS_4, SPAS_6, SPAS_7, SPAS_9, SPAS_10, SPAS_12, 
             SPAS_1.r, SPAS_2.r, SPAS_5.r, SPAS_8.r, SPAS_11.r  ))
```

```{r}
zoom_premeasures$SPA <- rowMeans(select(zoom_premeasures, SPAS_3, SPAS_4, SPAS_6, SPAS_7, SPAS_9, 
                                            SPAS_10, SPAS_12, SPAS_1.r, SPAS_2.r, SPAS_5.r, 
                                        SPAS_8.r, SPAS_11.r), na.rm = TRUE)

qplot(x=SPA, data=zoom_premeasures, bins=8)

zoom_premeasures <- zoom_premeasures %>%
  select(-SPAS_3, -SPAS_4, -SPAS_6, -SPAS_7, -SPAS_9, -SPAS_10, -SPAS_12, 
         -SPAS_1.r, -SPAS_2.r, -SPAS_5.r, -SPAS_8.r, -SPAS_11.r,
         -SPAS_1, -SPAS_2, -SPAS_5, -SPAS_8, -SPAS_11)
```

# Dialy Measures

```{r}
zoom_daily <- zoom_daily %>%
  select(Progress, ResponseId, `StroopTime_Congrue_First Click`:partID)
```


## Stroop Test - cognitive fatigue

```{r}
zoom_daily <- zoom_daily %>% 
  mutate(stroop_fatigue = `StroopTime_Incongru_Page Submit` - `StroopTime_Congrue_Page Submit`)

qplot(y=stroop_fatigue, x = Self_View, data=zoom_daily)

#remove greater than 100 or less than -100
zoom_daily <- zoom_daily %>% 
  mutate(stroop_fatigue = ifelse(stroop_fatigue <= 100 & stroop_fatigue >= -100, stroop_fatigue, NA))

qplot(y=stroop_fatigue, x = Self_View, data=zoom_daily)
```

## Zoom Use and Self-view Distraction

```{r}
table(zoom_daily$Zoom_Total_Mins) #what to do with days with NO zoom use?
table(zoom_daily$Self_View) #1 always use hide-self-view, 5 never used it

zoom_daily <- zoom_daily %>%
  mutate(Hide_Self_View_Today = 6 - Self_View,
         Self_View_Today = Self_View) %>%
  select(-Self_View)

table(zoom_daily$Self_View_Mins) #cleaning needed
800/60 #13 hours?? Does not correspond with Zoom minutes today
```

```{r}
zoom_daily <- zoom_daily %>%
  mutate(Self_Distraction_Today = 6 - Self_Distraction) %>%
  select(-Self_Distraction)
```


## Explicit Mental Fatigue

```{r}
corr.test(select(zoom_daily, Mental_Fatigue, ConcentrateDifficult, Memory_Problems, 
                 Slowness_of_Thinking, Sensitivity_to_Stres, Irritability))$r

alpha(select(zoom_daily, Mental_Fatigue, ConcentrateDifficult, Memory_Problems, 
                 Slowness_of_Thinking, Sensitivity_to_Stres, Irritability))  
```


```{r}
zoom_daily$Mental_Fatigue_Daily <- rowMeans(select(zoom_daily, Mental_Fatigue, ConcentrateDifficult, 
                                                   Memory_Problems, Slowness_of_Thinking, 
                                                   Sensitivity_to_Stres, Irritability), na.rm = TRUE)

qplot(x = Mental_Fatigue_Daily, data = zoom_daily, bins = 8)
```

## Explicit Physical Fatigue 

there is only one variable for physical fatigue, and it is on Mental fatique Scale block

```{r}
table(zoom_daily$Fatigue)
```


## Daily SSO (state self-obejtification)

```{r}
corr.test(select(zoom_daily, SSO_1, SSO_2, SSO_3))$r

alpha(select(zoom_daily, SSO_1, SSO_2, SSO_3))

zoom_daily$daily_SSO <- rowMeans(select(zoom_daily, SSO_1, SSO_2, SSO_3), na.rm = TRUE)

qplot(x = daily_SSO, data = zoom_daily, bins = 10)
table(zoom_daily$daily_SSO)

#Dichotomous
zoom_daily <- zoom_daily %>% 
  mutate(daily_SSO_binary = ifelse(daily_SSO == 1, 0, 1))

table(zoom_daily$daily_SSO_binary)
```

## Authenticity 

```{r}
corr.test(select(zoom_daily, SSO_4, SSO_5))$r

zoom_daily$authenticity <- rowMeans(select(zoom_daily, SSO_4, SSO_5), na.rm = TRUE)

qplot(x = authenticity, data = zoom_daily, bins = 8)
```

## Interaction Quality (reversed happy feelings)

```{r}
zoom_daily <- zoom_daily %>%
  mutate(interact_anxious.r = 8 - interact_anxious,
         interact_unhappy.r = 8 - interact_unhappy,
         interact_hostile.r = 8 - interac_hostile,
         interact_apprehensiv.r = 8 - interact_apprehensiv,
         interact_aggressive.r = 8 - interact_aggresive) 

  
corr.test(select(zoom_daily, interact_comfort, interact_anxious.r, interact_happy, interact_unhappy.r, 
                 interact_friendly, interact_warm, interact_easygoing, interact_hostile.r, 
                 interact_sincere, interact_authentic, interact_apprehensiv.r, interact_cooperative, 
                 interact_aggressive.r))$r

alpha(select(zoom_daily, interact_comfort, interact_anxious.r, interact_happy, interact_unhappy.r, 
                 interact_friendly, interact_warm, interact_easygoing, interact_hostile.r, 
                 interact_sincere, interact_authentic, interact_apprehensiv.r, interact_cooperative, 
                 interact_aggressive.r))

zoom_daily$interact_qual <- rowMeans(select(zoom_daily, interact_comfort, interact_anxious.r, 
                                              interact_happy, interact_unhappy.r, interact_friendly, 
                                              interact_warm, interact_easygoing, interact_hostile.r, 
                                              interact_sincere, interact_authentic, interact_apprehensiv.r,
                                              interact_cooperative, interact_aggressive.r), na.rm = TRUE)

qplot(x = interact_qual, data = zoom_daily, bins = 10)

zoom_daily <- zoom_daily %>%
  select(-(interact_comfort:interact_aggresive), -(interact_anxious.r:interact_aggressive.r))
```


# Daily Well Being 

## Well-being

```{r}
table(zoom_daily$How_Today)
```

## State Self-esteem (should separate positive and negative?)

```{r}
#I need to reverse the POSITIVE to get more self-esteem because 1 is strongly agree and 4 was strongly disagree. :(
zoom_daily <- zoom_daily %>%
  mutate(SES_Satisfied.r = 5 - SES_Satisfied, 
         SES_Good.r = 5 -  SES_Good,
         SES_Competent.r = 5 - SES_Competent, 
         SES_Worth.r = 5 - SES_Worth, 
         SES_Positive.r = 5 - SES_Positive)

corr.test(select(zoom_daily, SES_Satisfied.r, SES_Bad, SES_Good.r,
                 SES_Competent.r, SES_Proud, SES_Useless,
                 SES_Worth.r, SES_Respect, SES_Failure, SES_Positive.r))$r

alpha(select(zoom_daily, SES_Satisfied.r, SES_Bad, SES_Good.r,
                 SES_Competent.r, SES_Proud, SES_Useless,
                 SES_Worth.r, SES_Respect, SES_Failure, SES_Positive.r))

zoom_daily$SES_daily <- rowMeans(select(zoom_daily, SES_Satisfied.r, SES_Bad, SES_Good.r,
                 SES_Competent.r, SES_Proud, SES_Useless,
                 SES_Worth.r, SES_Respect, SES_Failure, SES_Positive.r), na.rm = TRUE)

qplot(x = SES_daily, data = zoom_daily, bins = 12)

names(zoom_daily)
zoom_daily <- zoom_daily %>%
  select(-(SES_Satisfied:SES_Positive), -(SES_Satisfied.r:SES_Positive.r))
```

# Joining datasets

```{r}
zoom_clean = right_join(zoom_premeasures, zoom_daily, by = "partID", keep = TRUE) %>%
  mutate(partID = partID.x) %>% select(-partID.y, -partID.x) %>%
  select(ResponseId.y, partID, day, Age:SES_daily)

names(zoom_clean)
glimpse(zoom_clean)
```

```{r}
write.csv(zoom_clean, "zoom_clean.csv")
```

