---
title             : "The Effects of Zoom Self-View Distraction on Daily Self-Objectification and Well-Being"
shorttitle        : "Zoom and Self-Obejctification"

author: 
  - name          : "Randi L. Garcia"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "College Lane, Smith College, Northampton, MA 01063"
    email         : "rgarcia@smith.edu"
    role:         
      - "Conceptualization"
      - "Methodology"          
      - "Formal Analysis"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
      - "Supervision"      
  - name          : "Jessica Pardim Araujo"
    affiliation   : "1"
    role:
      - "Writing - Original Draft Preparation"
      - "Formal Analysis"
      - "Writing - Review & Editing"
  - name          : "Pamala Kramer"
    affiliation   : "1"
    role:
      - "Formal Analysis"
      - "Writing - Review & Editing"  
  - name          : "Sarah Bingham"
    affiliation   : "1"
    role:
      - "Conceptualization"
      - "Methodology"        

affiliation:
  - id            : "1"
    institution   : "Psychology Department, Smith College"
  - id            : "2"
    institution   : "Program in Statistical and Data Sciences, Smith College"

authornote: |
  Smith College, Psychology Department, Smith College, Program in Statistical and Data Sciences.

abstract: |
  This study investigtaed the effects of using Zoom, specifically seeing oneself on Zoom on mental fatigue and general well-being. 
  
keywords          : "keywords"
wordcount         : "Zoom, self-objectification, computer mediated communication, authenticity"

bibliography      : ["r-references.bib", "psy-references.bib"]

floatsintext      : no
linenumbers       : no
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library(papaja)
library(readr)
library(tidyverse)
library(psych)
library(nlme)
library(lme4)
library(lmerTest)
r_refs("r-references.bib")
```

Zoom --> SSO --> Authenticity --> well-being (cognition, well-being)

# Introduction Outline 

1)
- Problem 
- Literature 
  - Zoom Fatigue 
  - Close paper on zoom and trait objectification 
  
- Gap we are filling
  - 5-day daily diaries
  - State self-objectification
  
2)
- Computer mediated interaction and self-objectification
  - Social media
  - Video chat (e.g Skype)
  
- State Self-Objectification
  - Authenticity
  - Well-being and cognition
  
3)
- Zoom and well-being
  - Zoom fatigue 
  - Cognitive fatigue
  
4)
- Explaining reasons for the negative effects of Zoom
  - Self-objectification
  - Seeing yourself
  - Authenticity
  - Studies on self-verification; studies using mirror.



Past studies have found that using Zoom can cause mental fatigue [@bailenson2021nonverbal]. Seeing oneself on Zoom has also been linked to appearance concerns [@pfund2020video].

# Methods

## Participants

## Measures

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

```{r}
zoom_clean <- read_csv("zoom_clean.csv")
#names(zoom_clean)
```

## Zoom Use and State Self-Objectification

```{r}
corr.test(select(zoom_clean, daily_SSO, daily_SSO_binary, tso_mean, OBCS_sur, SPA, Zoom_Total_Mins, Zoom_Use_Weekly, Zoom_Use_Daily, Hide_Self_View, Image_Distraction, Hide_Self_View_Today, Self_Distraction_Today))$r
```

```{r}
glmer_ssozoom <- glmer(daily_SSO_binary ~ day + Zoom_Total_Mins + (1|partID), 
                    family=binomial, 
                    data = zoom_clean)

summary(glmer_ssozoom)
#confint(glmer_ssozoom)

#### TRYING LMER MODELS WITH daily_SSO even though assumptions of normality are violated
mlm_mod_int <- lmer(daily_SSO ~ day + Zoom_Total_Mins + (1|partID), data = zoom_clean)
summary(mlm_mod_int)
mlm_mod_int <- lmer(daily_SSO ~ day + Hide_Self_View_Today + Self_Distraction_Today + (1|partID), data = zoom_clean)
summary(mlm_mod_int)
plot(mlm_mod_int)
```

```{r}
# Zoom_Total_Mins
# Self_View_Mins
# Hide_Self_View_Today
# Self_View_Today
# Self_Distraction_Today

glmer_ssohide <- glmer(daily_SSO_binary ~ day + Hide_Self_View_Today + Self_Distraction_Today 
                       + (1|partID), 
                    family=binomial, 
                    data = zoom_clean)

summary(glmer_ssohide)
```

Interaction with TSO 

```{r}
glmer_ssohide <- glmer(daily_SSO_binary ~ day + Hide_Self_View_Today*OBCS_sur + Self_Distraction_Today*OBCS_sur 
                       + (1|partID), 
                    family=binomial, 
                    data = zoom_clean)

summary(glmer_ssohide)

glmer_ssohide <- glmer(daily_SSO_binary ~ day + Hide_Self_View_Today + Self_Distraction_Today + OBCS_sur
                       + (1|partID), 
                    family=binomial, 
                    data = zoom_clean)

summary(glmer_ssohide)
```

```{r}
glmer_ssohide <- glmer(daily_SSO_binary ~ day + Hide_Self_View_Today*tso_mean + Self_Distraction_Today*tso_mean 
                       + (1|partID), 
                    family=binomial, 
                    data = zoom_clean)

summary(glmer_ssohide)

glmer_ssohide <- glmer(daily_SSO_binary ~ day + Hide_Self_View_Today + Self_Distraction_Today + tso_mean
                       + (1|partID), 
                    family=binomial, 
                    data = zoom_clean)

summary(glmer_ssohide)
```

```{r}
#does not converge with BOTH interactions in the model
glmer_ssohide <- glmer(daily_SSO_binary ~ day + Hide_Self_View_Today + Self_Distraction_Today*SPA
                       + (1|partID), 
                    family=binomial, 
                    data = zoom_clean)


summary(glmer_ssohide)

glmer_ssohide <- glmer(daily_SSO_binary ~ day + Hide_Self_View_Today + Self_Distraction_Today + SPA
                       + (1|partID), 
                    family=binomial, 
                    data = zoom_clean)

summary(glmer_ssohide)
```

## Daliy State Self-Objectification and Outcomes

```{r}
corr.test(select(zoom_clean, daily_SSO, daily_SSO_binary, stroop_fatigue, How_Today, 
                 Mental_Fatigue_Daily, authenticity, interact_qual, SES_daily))$r
```

State Self-Objectification to authenticity and interaction quality. 

```{r}
mlm_mod_int <- lmer(authenticity ~ daily_SSO + day
                         + (1|partID), 
                         data = zoom_clean)
summary(mlm_mod_int)
plot(mlm_mod_int)
#confint(mlm_mod_int)

mlm_mod_int <- lmer(interact_qual ~ daily_SSO + day
                         + (1|partID), 
                         data = zoom_clean)
summary(mlm_mod_int)
```

Interaction quality (and SSO) and Well-Being

```{r}
mlm_mod_int <- lmer(stroop_fatigue ~ authenticity + daily_SSO + day + (1|partID), data = zoom_clean)
mlm_mod_int <- lmer(stroop_fatigue ~ interact_qual + daily_SSO + day + (1|partID), data = zoom_clean)
summary(mlm_mod_int)

mlm_mod_int <- lmer(How_Today ~ authenticity + daily_SSO + day + (1|partID), data = zoom_clean)
mlm_mod_int <- lmer(How_Today ~ interact_qual + daily_SSO + day + (1|partID), data = zoom_clean)
summary(mlm_mod_int)

mlm_mod_int <- lmer(Mental_Fatigue_Daily ~ authenticity + daily_SSO + day + (1|partID), data = zoom_clean)
mlm_mod_int <- lmer(Mental_Fatigue_Daily ~ interact_qual + daily_SSO + day + (1|partID), data = zoom_clean)
summary(mlm_mod_int)

mlm_mod_int <- lmer(SES_daily ~ authenticity + daily_SSO + day + (1|partID), data = zoom_clean)
mlm_mod_int <- lmer(SES_daily ~ interact_qual + daily_SSO + day + (1|partID), data = zoom_clean)
summary(mlm_mod_int)
```


# Discussion


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
